The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-10 paper/ms.tex
Replace 3 JR Jphi figures with 1 figure

In Figure~\ref{fig:JR_zerr_hist} we plot the distribution of $J_R$ as a function of orbital phase induced by an offset in $z$, and in Figures~\ref{fig:JR_xerr_hist} and
\ref{fig:Jphi_xerr_hist} we plot the $J_R$ and $J_{\phi}$
distributions induced by an offset in $x$. We plot the distributions for the
thick-disk (top panels) and thin-disk (bottom panels) orbits.

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.35224200913in]{fig/schmactions_JR_zerr_hist.pdf}
\end{center}
\caption{A histogram of the values computed for $J_R$ for the thick-disk (top
panel) and thin-disk (bottom panel) orbits assuming a $z$ offset of
$100\,\pc$. The induced error distribution more closely resembles a Gaussian
centered on the null value.}
\label{fig:JR_zerr_hist}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.35224200913in]{fig/schmactions_JR_xerr_hist.pdf}
\end{center}
\caption{A histogram of the values computed for $J_R$ for the thick-disk (top
panel) and thin-disk (bottom panel) orbits assuming a $x$ offset of
$100\,\pc$. The induced error distribution is non-Gaussian and bimodal, with
neither of the modes centered on null.}
\label{fig:JR_xerr_hist}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.35224200913in]{fig/schmactions_Jphi_xerr_hist.pdf}
\end{center}
\caption{A histogram of the values computed for $J_{\phi}$ for the thick-disk
(top panel) and thin-disk (bottom panel) orbits assuming a $z$ offset of
$100\,\pc$. The induced error distribution is non-Gaussian and bimodal, with
neither of the modes centered on null.}
\label{fig:Jphi_xerr_hist}
\end{figure}

>>>>

In Figure~\ref{fig:Jphi_JR_hist} we plot the distribution of $J_R$ as a
function of orbital phase induced by an offset in $x$ and $z$ and the
distribution of $J_{\phi}$ for an offset in $x$. We plot the distributions for
the thick-disk (upper panels) and thin-disk (lower panels) orbits.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=7.10000594991in]{fig/schmactions_Jphi_JR_hist.pdf}
\end{center}
\caption{A histogram of the values computed for $J_R$ and $J_{\phi}$ for the
thick-disk (upper panels) and thin-disk (lower panels). For $J_R$ we assume an
$x$ offset (left) and $z$ offset (center) of $100\,\pc$, while for $J_{\phi}$
we consider only an $x$ offset (right). In each panel the true value is given
by a vertical dashed line. The induced error distribution in $J_R$ for an $x$
offset more closely resembles a Gaussian centered on the null value, but not
for the other two offsets considered.}
\label{fig:Jphi_JR_hist}
\end{figure*}
